Notebook of learning from ensemble labels

### 2021-08-16 docs/notebook_learn_dl_ensemble.Rmd
Remove an assert check

Prepare work:

```
scp -r /Volumes/wildebeest/dl_train ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp -r /Volumes/wildebeest/dl_valid ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
```

@@

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 221 --tain_batch_size 16
```

@@

```
python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
```

@@

python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

```
scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/final.pth ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/final.pth;
scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/args.pkl ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/args.pkl

python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

>>>>

Parse dataset:

```
./hrlcm/utils/parse_dataset.sh results/north
```

@@

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

@@

@@

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl
```

@@

python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard12_clr_200epc' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
